---
title: "ToothGrowth by Dose and Delivery Method "
---


## Load and visualize the data

```{r results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
data(ToothGrowth)
str(ToothGrowth)
head(ToothGrowth)
```

## Summary of the data
```{r , echo=FALSE}
summary(ToothGrowth)
unique(ToothGrowth$supp)
unique(ToothGrowth$len)
unique(ToothGrowth$dose)
```
We will create graphs to see ToothGrowth by dose and supplement (Delivery method)
```{r}
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
ggplot(aes(x=dose, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=dose)) + xlab("Dose Amount") + ylab("Tooth Length") + facet_grid(~ supp) + ggtitle("Tooth Length vs. Dose Amount \nby Delivery Method") + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
```
```{r}
# Plot tooth length ('len') vs. supplement delivery method ('supp') broken out by the dose amount ('dose')
ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp)) + xlab("Supplement Delivery") + ylab("Tooth Length") + facet_grid(~ dose) + ggtitle("Tooth Length vs. Delivery Method \nby Dose Amount") + 
     theme(plot.title = element_text(lineheight=.8, face="bold"))
```

## We will compare tooth growth with supplement OJ,VC using a t-test.
```{r}
t.test(len~supp,data=ToothGrowth)
```
The p-value  0.06, and the confidence interval contains zero,indicates  that the different supplement types have no effect on tooth length.

##Confidence Intervals and/or hypothesis tests to compare tooth growth between dose levels.
```{r}
dose1 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
dose2 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))
dose3 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))
t.test(len ~ dose, paired = F, var.equal = F, data = dose1)
t.test(len ~ dose, paired = F, var.equal = F, data = dose2)
t.test(len ~ dose, paired = F, var.equal = F, data = dose3)
```
## Correlation between dose level and change in tooth growth within each dose level.
```{r}
Tooth.dose4 <- subset(ToothGrowth, dose == 0.5)
Tooth.dose5 <- subset(ToothGrowth, dose == 1.0)
Tooth.dose6 <- subset(ToothGrowth, dose == 2.0)
t.test(len ~ supp, paired = F, var.equal = F, data = Tooth.dose4)
t.test(len ~ supp, paired = F, var.equal = F, data = Tooth.dose5)
t.test(len ~ supp, paired = F, var.equal = F, data = Tooth.dose6)
```
We can conclude  following:
1.The supplement delivery method has no effect on tooth growth/length
2.Increased dosages do result in increased tooth length.
3.The sample is representative of the population
4.The distribution of the sample means follows the Central Limit Theorem
