## Statistical Inference- Part 1
Kalpana Rupani

## Overview
This is part 1 of Coursera Statistical Inference course project. This  simulation exercise,investigates the distribution of averages of 40 exponentials with a thousand simulations and the exponential distribution in R and compares it with the Central Limit Theorem. This  simulation illustrates the following :

1. the sample mean and the theoretical mean
2. the sample variance and the theoretical variance
3. the distribution


## Simulation
The exponential distribution is simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations.

```{r}
# set seed for reproducability
set.seed(2016)

# Set sampling values as described in the project instructions
lambda <- 0.2   # lambda

n <- 40         # number of exponentials

simulations <- 1000    # number of simulations

#Run simulations
simulated_exponential <- replicate(simulations, rexp(n, lambda))

#Calc the means of the exponential simulations
means_exp <- apply(simulated_exponential, 2, mean)

#Histogram of the means

hist(means_exp, breaks=40, xlim = c(2,9), main="Exponential Function Simulation Means", col = "orange")


```

## Sample Mean vs. Theoretical Mean

```{r}
sample_mean <- mean(means_exp)
cat("sample mean: ", sample_mean)
theoretical_mean <- 1/lambda
cat("theoretical mean: ", theoretical_mean)
```
## Sample Variance vs. Theoretical Variance
```{r}
sample_var <- var(means_exp)
cat("sample variance: ", sample_var)
theoretical_var <- (1/lambda)^2/n
cat("theoretical variance: ", theoretical_var)
```
##Distribution
Finally, we’ll investigate whether the exponential distribution is approximately normal. Due to the Central Limit Theorem, the means of the sample simulations should follow a normal distribution.

```{r}
hist(means_exp, prob=TRUE, col="grey", main="Exponential Function Simulation Means", breaks=40, xlim=c(2,9), xlab = "Simulation Means")
lines(density(means_exp), lwd=3, col="green")

x <- seq(min(means_exp), max(means_exp), length=2*n)
y <- dnorm(x, mean=1/lambda, sd=sqrt(((1/lambda)/sqrt(n))^2))
lines(x, y, pch=20, col="red", lwd=2, lty = 2)
```